Hardware-Accelerated Rendering of Intersecting Volumes using Boolean Operations

### 2013-06-24 paper.tex
Venn diagrams for Boolean operations
Just say depth-masking instead of depth-buffer masking

The boolean operations involved are AND and XOR.  AND takes the intersection of
two shapes, while XOR, meaning exclusive OR, takes everything but the
intersection.

@@

\section{Boolean AND with Depth Buffer Masking}

@@

\begin{figure}
\centering
\includegraphics[width=0.8\textwidth]{boolean-and.pdf}
\caption{
Top-down view of rendering intersecting volumes using the Boolean AND with depth
buffer masking approach.  First the part of the volume directly behind the
intersection, colored red, is rendered.  Next the intersection, colored green,
is rendered.  Then the the part of the volume directly in front of the
intersection, colored blue, is rendered.  Finally the depth buffer is masked off
using the Boolean AND so that when the cubes are rendered again, only the parts
colored yellow are rendered.
}
\label{boolean-and}
\end{figure}

>>>>

The boolean operations involved are AND and XOR.  AND takes the intersection of
two shapes, while XOR, meaning exclusive OR, takes everything but the
intersection.  Figures \ref{boolean-and-venn-diagram} and
\ref{boolean-xor-venn-diagram} show the Boolean AND and Boolean XOR operations
as Venn diagrams.

\begin{figure}
\centering
\includegraphics[width=0.9\textwidth]{venn-and.pdf}
\caption{Boolean AND.}
\label{boolean-and-venn-diagram}
\end{figure}

\begin{figure}
\centering
\includegraphics[width=0.9\textwidth]{venn-xor.pdf}
\caption{Boolean XOR.}
\label{boolean-xor-venn-diagram}
\end{figure}

@@

\section{Boolean AND with Depth-Masking}

@@

\begin{figure}
\centering
\includegraphics[width=0.8\textwidth]{boolean-and.pdf}
\caption{
Top-down view of rendering intersecting volumes using the Boolean AND with
depth-masking approach.  First the part of the volume directly behind the
intersection, colored red, is rendered.  Next the intersection, colored green,
is rendered.  Then the the part of the volume directly in front of the
intersection, colored blue, is rendered.  Finally the depth buffer is masked off
using the Boolean AND so that when the cubes are rendered again, only the parts
colored yellow are rendered.
}
\label{boolean-and}
\end{figure}
